Covariate analysis of CMC RNASeq data reprocessed with STAR-feature counts workflow with Ensembl v75 (ACC and DLPFC with CQN normlaisation)

### 2017-06-19 code/Rmd/CMC_ACC_DLPFC_STAR_ENSEMBL_v75_CQN.Rmd
Minor bug fix

### Identify gene outliers
Set outlier expression of genes in each samples to NA
```{r detect.outlier.genes}
LOG.CPM = cpm(PROCESSED_COUNTS$filteredExprMatrix$counts, log = T)

@@

plotdata <- left_join(plotdata, rownameToFirstColumn(COVARIATES, 'SampleID')) %>%
  tidyr::separate(Dx.Tissue, c('Dx','Tissue'), sep = '_')
plotdata$label = plotdata$SampleID
plotdata$label[!(plotdata$label %in% top.nasamples)] = ''

>>>>

### Identify gene outliers
Set outlier expression of genes in each samples to NA
```{r detect.outlier.genes, cache = FALSE}
LOG.CPM = cpm(PROCESSED_COUNTS$filteredExprMatrix$counts, log = T)

@@

plotdata <- left_join(plotdata, rownameToFirstColumn(COVARIATES, 'SampleID')) %>%
  tidyr::separate(Dx.Tissue, c('Dx','Tissue'), sep = '_')
plotdata$label = plotdata$SampleID
plotdata$label[!(plotdata$label %in% top.nsamples)] = ''
